This is an example of article title

### 2024-09-03 paper/paper.tex
Minor shortifications

%- Some information on peridynamic material models
The general internal force density for state-based peridynamics is defined as
\begin{equation}
\vb{b}^{\mathrm{int}} (\vb{X},t) = \int_\mathcal{H} \vb{t} - \vb{t}' \; \mathrm{d}V' \; ,
\end{equation}
with the \emph{force vector states} $\vb{t}=\vb{t}(\vb{\Delta X}, t)$ and $\vb{t}'=\vb{t}(-\vb{\Delta X}, t)$.
In the first original bond-based formulation of peridynamics, the force vector states $\vb{t}$ and  $\vb{t}'$ have the same value and opposite direction.
This implies intrinsic limitation to only one material parameter and in consequence to restrictions on the Poisson's ratio \cite{Silling2007,Trageser2020}.
To overcome these restrictions, a state-based peridynamics was established.
In the ordinary state-based peridynamics, the deformation states of neighboring points also influence the internal force density \cite{Silling2007}.
This leads to force vector states which are still collinear but not of same value anymore.

@@

\section{Perspectives}
In version \texttt{v0.2.0}, a multithreading approach is employed.
An extension to a hybrid approach with MPI or multithreading is made in version \texttt{v0.3.0}.
The internals have been thoroughly reworked to incorporate a data structure that can be used for parallel simulations with either MPI or multithreading.
These changes also include new material models and a simplified API with streamlined internal structures.
For future versions it is planned to add improved material models and to utilize \texttt{DifferentialEquations.jl} for the time integration.

>>>>

%- Some information on peridynamic material models
The general internal force density for state-based peridynamics is defined as
\begin{equation}
\vb{b}^{\mathrm{int}} (\vb{X},t) = \int_\mathcal{H} \vb{t} - \vb{t}' \; \mathrm{d}V' \; ,
\end{equation}
with the \emph{force vector states} $\vb{t}=\vb{t}(\vb{\Delta X}, t)$ and $\vb{t}'=\vb{t}(-\vb{\Delta X}, t)$.
In the first original bond-based formulation of peridynamics, the force vector states $\vb{t}$ and  $\vb{t}'$ have the same value and opposite direction.
This implies intrinsic limitation to only one material parameter and in consequence to restrictions on the Poisson's ratio \cite{Silling2007}.
To overcome these restrictions, a state-based peridynamics was established.
In the ordinary state-based peridynamics, the deformation states of neighboring points also influence the internal force density \cite{Silling2007}.
This leads to force vector states which are still collinear but not of same value anymore.

@@

\section{Perspectives}
In version \texttt{v0.2.0}, a multithreading approach is employed.
An extension to a hybrid approach with MPI or multithreading is made in version \texttt{v0.3.0}.
The internals have been thoroughly reworked to incorporate a data structure that can be used for parallel simulations with either MPI or multithreading.
These changes also include new material models and a simplified API.
For future versions it is planned to add improved material models and to utilize \texttt{DifferentialEquations.jl} for the time integration.
